---
date: Updated "`r format(Sys.time(), '%d %B %Y')`"
fig_caption: yes
incremental: true
output: ioslides_presentation

---

# Model Ins and Outs 

## 

read.csv(file='...')

> - read.scor
> - read.enam
> - read.wand
> - read.nea
> - read.EcoNet

## 

pack(flow, input, respiration, export, output, storage, living)


## 

pack(flow, input, respiration, export, output, storage, living)

unpack(x='network object')


## Micro-modeling (Exercise 1)

M = {F, z, e, r, X, Living}


## Micro-modeling (Exercise 1)

M = {F, z, e, r, X, Living}

1. Draw a network model as a flow diagram with 3 nodes

## Micro-modeling (Exercise 1)

M = {F, z, e, r, X, Living}

1. Draw a network model as a flow diagram with 3 nodes
2. Create objects for each of your model components
3. "Pack" your model into a network object
4. "Unpack" your network and look at the parts
5. Plot
6. Investigate some network metric you're interested in


## Micro-modeling (Solution 1)

```{r ,results='hide'}

F <- c(0,5,0,
       0,0,1,
       0,0,0)
F <- matrix(F,nrow=3,byrow=TRUE)
z <- c(10,0,0)
e <- c(3,3,3)
r <-c(1,1,1)
X <- c(10,3,1)
liv <- c(TRUE,TRUE,FALSE)
toy <- pack(F,z,e,r,X,liv)
enaFlow(toy)

```

## reading models (Exercise 2)

0. Download Mdloti Estuary model (Scharler 2012)
1. Read in the Mdloti model (read.enam)
2. Check if the model is balanced
3. Get the throughflow values
4. Make a plot with nodes scaled by throughflow

## reading models (Solution 2)

```{r ,results='hide'}

mdloti <- read.enam('http://people.uncw.edu/borretts/data/MDMAR02.xlsx')
mdloti
Tf <- enaFlow(mdloti)$T
Tf.rel <- Tf/max(Tf)
plot(mdloti,vertex.cex=Tf.rel,
     gmode='graph',displaylab=T,arrowhead.cex=0)

```


